Automated detection of data fabrication using statistical tools

### 2018-03-28 submission/redraft.rmd
Add paragraph

>>>>

# Study 1 - detecting fabricated summary statistics

We tested the performance of statistical methods to detect data fabrication in summary statistics with genuine- and fabricated summary statistics from four anchoring studies [@10.1126/science.185.4157.1124;@10.1037/e722982011-058]. 
The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity. 
For example 'Do you think the percentage of African countries in the UN is above or below  [10\% or 65\%]?  What do you think is the percentage of African countries in the UN?'. 
These questions yield mean responses of 25\% and 45\%, respectively [@10.1126/science.185.4157.1124], despite essentially posing the same factual question. 
A considerable amount of (assumably) genuine data sets on the anchoring  heuristic are freely available [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178] and we collected fabricated data sets within this study. 
This study was approved by the Tilburg Ethical Review Board (EC-2015.50).
